Index measures for oak decline severity using phenotypic descriptors

### 2020-02-07 manuscript/manuscript.Rmd
added author affiliations, line numbers and line spacing

---
title: "Index measures for oak decline severity using phenotypic descriptors"
output: 
  word_document: default
  pdf_document: default
bibliography: references.bib
---

@@

**Authors:** Jasen Finch, Nathan Brown, John Draper & Sandra Denman

**Proposed journal:** Still undecided! ??Plant Methods, Forestry??

>>>>

---
output: 
  word_document: default
  pdf_document: default
header-includes:
  - \linespread{2}
  - \usepackage{lineno}
  - \linenumbers
bibliography: references.bib
---

@@

**Proposed journal:** (1) Forest Ecology & Management (2) Forestry (3) European Journal of Forest Research (4) Plant Methods

# Title: Index measures for oak decline severity using phenotypic descriptors

**Authors:** Jasen Finch^1\*^, Nathan Brown^2^, Manfred Beckmann^1^, Sandra Denman^2^ & John Draper^1^

^\*^ Corresponding author

**Addresses:**

1. Institute of biological, environmental and rural sciences, Aberystwyth University, Aberystwyth, SY23 3DA, UK

2. Centre for Forestry and Climate Change, Forest Research, Alice Holt Lodge, Farnham GU 4LH, UK
